Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
Cosmit.
Remove remark on collaborative filtering.
Nicolas will work on matrix completion during his GSOC, which can be
used to do for collaborative filtering.
Cosmit conclusion.

Within the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications, successes in various machine learning
challenges (e.g., Kaggle), or significant statistics derived from our
repositories and mailing lists.  At the time of writing, the project is watched
by 1309 people and forked 667 times on GitHub, and the mailing-list receives
more than 300 mails per month. The version control logs for the development
version
% ddaa494c116e3c16bf032003c5cccbed851733d2
also count 183 contributors to the project (after manual deduplication).

@@

Although it is coming close to a 1.0 release, the \sklearn toolkit is by no
means finished. At the time, it does not support all tasks in the broad field of
machine learning, but does not intend to either. Among others, missing features
include neural networks, ensemble meta-estimators for bagging or subsampling
strategies, or missing value completion algorithms provided as transformers.
However, topics like structured prediction or reinforcement learning are
considered off-topic for the project. The library also does not provide any
collaborative filtering algorithms -- it remains to be seen whether a compatible
and matching API can be written for them.

>>>>

Within the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications, successes in various machine learning
challenges (e.g., Kaggle), or significant statistics derived from our
repositories and mailing lists.  At the time of writing, the project is watched
by 1309 people and forked 667 times on GitHub, and the mailing-list receives
more than 300 mails per month. The version control logs for the development
version
% ddaa494c116e3c16bf032003c5cccbed851733d2
also count 183 unique contributors to the project.

@@

Although it is coming close to a 1.0 release, \sklearn is by no means finished.
At the time, it does not support many classical machine learning tasks. Among
others, missing features include neural networks, ensemble meta-estimators for
bagging or subsampling strategies, or missing value completion algorithms
provided as transformers.  However, topics like structured prediction or
reinforcement learning are considered off-topic for the project, since they
would require quite different data representations and API.
